---
title: "Age of Empires IV: Tournament Results by Country"
author: "Yi Zhang"
date: 2026-09-26
format: html
---

## Data and questions

This post uses the player and tournament-result tables for [Red Bull Wololo: Legacy 2022 – Age of Empires IV](https://www.esportsearnings.com/tournaments/56552-red-bull-wololo-legacy-2022-age-of-empires-iv). It asks which countries were represented, what placements their players achieved, and how much prize money they received.

The code below is the initial working scaffold for the analysis. The two tables are kept separate until the join step so that the data relationship remains explicit.

```{r}
#| label: setup-data
#| message: false

player_profiles <- data.frame(
  player_id = c("marinelord", "themista", "beastyqt", "lucifron", "1puppypaw", "iammagic", "leenock", "recon", "capoch", "demu", "theviper", "vortix", "hut", "kasva", "sortof", "wam01"),
  player_name = c("MarineLorD", "TheMista", "Beastyqt", "LucifroN", "1puppypaw", "IamMagic", "Leenock", "RecoN", "Capoch", "DeMu", "TheViper", "VortiX", "HuT", "Kasva", "SortOf", "Wam01"),
  country = c("France", "Greece", "Serbia", "Spain", "Canada", "Canada", "Korea, Republic of", "United Kingdom", "Argentina", "United Kingdom", "Norway", "Spain", "Australia", "Turkey", "Sweden", "Canada"),
  stringsAsFactors = FALSE
)

tournament_results <- data.frame(
  player_id = player_profiles$player_id,
  placement = c("1st", "2nd", "3rd-4th", "3rd-4th", "5th-8th", "5th-8th", "5th-8th", "5th-8th", "9th-12th", "9th-12th", "9th-12th", "9th-12th", "13th-16th", "13th-16th", "13th-16th", "13th-16th"),
  prize_usd = c(100000, 50000, 20000, 20000, 12500, 12500, 12500, 12500, 9000, 9000, 9000, 9000, 6000, 6000, 6000, 6000)
)

head(player_profiles)
```

## Joining and summarising the tables

```{r}
#| label: joined-summary

joined_results <- merge(tournament_results, player_profiles, by = "player_id")
country_summary <- aggregate(
  prize_usd ~ country,
  data = joined_results,
  FUN = sum
)
country_summary$players <- as.integer(
  table(joined_results$country)[country_summary$country]
)
country_summary <- country_summary[, c("country", "players", "prize_usd")]

country_summary[order(-country_summary$players), ]
```

The joined table connects each player to a country, placement, and prize amount. The country summary provides the first answer to the three project questions: representation, placements, and prize money.

## Prize money by country

```{r}
#| label: fig-r-prize-by-country
#| fig-cap: "Prize money awarded to players from each country."

barplot(
  country_summary$prize_usd,
  names.arg = country_summary$country,
  las = 2,
  cex.names = 0.7,
  ylab = "Prize money (USD)",
  main = "AoE4 prize money by country"
)
```
